---
title: "Exploratory Analysis"
author: "Daniel Alcaraz"
date: "8 de marzo de 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(purrr)
library(tibble)
library(dplyr)
library(readr)
library(tidyr)
Gathered_tidy_data <- read_csv("Gathered_tidy_data.csv", 
col_types = cols(X1 = col_skip()))

```

## Spanish gender paygap analysis

The main objective of this repository is to analyze the gender paygap by gender in Spain. It is motivated by the more than obvious wage differences between men and women, and it is my particular way of shedding some light on this fact. In addition, a law was recently passed in Spain requiring companies to publish the salaries of their workers divided into categories. This law also adds that if the wage gap is mś of 25%, the wage gap will be considered to be due to gender unless proven otherwise. Thus, this research will provide an exploratory analysis first, and later a regression study to try to show that the wage differences are not (or are) due to gender.

```{r,echo=FALSE}
Grouped_Basic_salary<-Gathered_tidy_data %>%
  filter(`Wage Type`=='Basic Salary') %>%
  group_by(Gender)

ggplot(data = Grouped_Basic_salary)+
  geom_bar(mapping = aes(x=`Autonomous Region`,y=Quantity,fill=Gender),stat = 'identity',position = 'dodge') + coord_flip() + ggtitle('Basic salary by gender and Autonomous Region')

```

